Open-source landscape for 3D CSEM modelling

### 2020-05-25 manuscript/Manuscript.tex

% Remove once done
\usepackage[textsize=footnotesize, textwidth=2.8cm]{todonotes}

@@

\itodo{
  For comments in the margin, use:\\[.2cm]
  \qquad\texttt{\textbackslash mycom[YOURINITIALS]\{comment\}}\\[.2cm]
  and for inline comments, use:\\[.2cm]
  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}
}

@@

\imycom[RR]{We need to take care to not mix British English with AE, I'm very
  used to AE, but Dieter started with (at least what I can identify) mainly BE,
  so I tried to follow (mainly s instead of z and ou instead of o in some
  words). I hope there are not too many inconsistencies, as probably Lindsey
  has to fix all these mistakes in the end:-)}
\imycom[DW]{Be aware of Canadian English and Australian English :-D -- You are
  of course right. I am usually mostly BE, having done my PhD in Scotland.
  However, I don't think it matters at the moment, because it will depend to
  what journal we submit. With an appropriate spellchecker that should be a
  quick thing then.}

Controlled-source electromagnetic (CSEM) measurements are a frequently applied
method in various geophysical exploration fields, such as geothermal and
groundwater, oil and gas, mining, civil engineering, or geo-hazards. Modelling
these electromagnetic fields is therefore of great interest to design survey
layouts, understand the measured data and inversion purposes. Publications
regarding 3D modelling in electromagnetic methods started to appear as early as
the 1970's and 1980's. These early publications were integral equation (IE)
methods, having an anomaly embedded within a layered medium, mostly for
loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann,
GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements
\citep{GEO.84.Wannamaker}.

@@

Probably the main reason for the numerous amount of code developments was
already outlined by \cite{SG.05.Avdeev}, who finished his review with the
following statement: «\emph{The most important challenge that faces the EM
community today is to convince software developers to put their 3-D EM forward
and inverse solutions into the public domain, at least after some time. This
would have a strong impact on the whole subject and the developers would
benefit from feedback regarding the real needs of the end-users.}» Some major
exploration service companies as well as certain research consortia and
research groups own their 3D CSEM codes, but how about codes that are
open-source? Academic codes were traditionally often available upon request by
authors. Codes distributed that way were often provided with the request to not
share the code, and they often come without a license attached which means that
they are not open-source. Also, at times there can be significant hurdles to
install a code.

The meaning of the term open-source evolved rapidly in the last two decades.
Today, open-source generally not only means that a code is available (with a
proper license), but also that the code is hosted online, is under version
control, has the possibility to file issues and make pull requests to fix bugs.
These are important requirements for reproducible research «\emph{to provide
the means by which the reader can verify the validity of the results and make
use of them in further research}» \citep{GEO.17.Broggini}. Well maintained
codes often have continuous integration that includes testing of the code base
and online hosted documentation, often including examples and tutorials. As
such, the term has shifted from purely open-source codes to developments in the
open with increasingly building a global community. Related projects within the
realm of geophysical exploration are e.g., pyGIMLi \citep{CAG.17.Rucker} or
Fatiando \citep{JOSS.18.Uieda}. \mycom[DW]{Others coming to your
mind?}\mycom[RR]{no thoughts about geophysics, but there are many projects for
related topics such as gmt, gis, mesh-gen}

\imycom[RR]{i suggest to use also "emph" style for all other package names, not
only ours}

@@

We simulate EM fields for a layered background model with vertical transverse
isotropy, containing three blocks, and the complex marine Marlim R3D model.
These two model designs as well as the corresponding results from four
different codes provide a benchmark for new codes to be compared to and
validated with. In the following section, we introduce the codes under
consideration. Afterwards, we present the considered benchmark cases in detail
and present the modeling results of our four codes in terms of accuracy and
computational performance. Beyond that, we extensively discuss important points
that control the performance and suitability of our FD and FE codes, including
mainly considerations about the mesh design and the choice of solvers. We
conclude with a summary of our results and a motivation for the EM community to
continue not only extending the landscape of open-source codes and also
creating a landscape of open-source benchmark models.

\imycom[RR]{Regarding "It is worth mentioning that there are many more 3D EM
  codes developed in other fields than geophysics such as communication systems
  (antennas, radar, satellites), medical imaging, or civil engineering. There
  are various open-source codes in these fields too, e.g., Elmer ([DW]: Add 2-3
  proper references) (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't
  find a publication, just a poster). While these codes could potentially be
  used for the same goals as presented here we restrict our review to codes
  purpose-built and ready without further adjustments for geophysical
  applications."

  I thought a lot about this but I just think the previous paragraph is not
  required in our introduction and haven't find a location where it fits
  considering different logical structures. I think it is also not important
  for this paper to tell "that there are more codes in EM than only
  geophysics", that's quite obvious. Maybe delete or shorten to 1 sentences to
  add Elmer and place this sentence somewhere else? I think, an appropriate
  list of all non-geophysical open-source EM codes should be very long anyway,
  we just don't know them or at least I'm not familiar with them.}

@@

\imycom[RR]{too much info (redundancy to text) for table caption}

\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations
  in its differential form (DE) under the quasistatic approximation. Note that
  \emg3d is a solver on its own, while the other codes implement third-package
  solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS}
  \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & PMC; PEC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

We computed the responses for two different models to verify that all different
3D codes yield the same electromagnetic responses. The first simple Block model
consists of a layered, anisotropic background with three embedded blocks. The
second Marlim R3D model is based on a very complex, realistic marine CSEM
setup.

\subsection{Block model}

\imycom[RR]{I think the miensopust argument is rather suited to motivate our
work in the introduction, i hope its fine that i moved this argument}

@@

Figure~\ref{fig:results-layered-0} illustrates the inline responses in the
top-row for offsets $r>0.5\,$km. We only show the semi-analytical result for
the real and imaginary amplitudes. The bottom row displays the relative error
of the 3D codes. The results show that all codes are yielding accurate result
with errors of around 1\,\% in most parts and overall below a few percent,
disregarding locations affected by sign reversals. The differences can be
mainly attributed to the chosen discretisations. The FE codes show the
strongest misfits at large offsets, most likely caused by the utilized boundary
mesh, whereas \emg3d seems to do a very good job\mycom[RR]{maybe reformulate to
something like: whereas emg3d appears to be not affected by boundary effects}.
Close to the 200\,m long source, emg3d is less precise which is attributed to
comparatively large cell sizes in this region.
%
\plot*{results-layered-0}{width=.8\textwidth}{
   Comparison of the layered model for the inline receivers ($y=0\,$km).
   Top row shows the semi-analytical responses from \empymod, and bottom row
   shows the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
}
%

@@

In a second step, three resistive blocks were added in the 3.3\,km-thick,
anisotropic background layer as shown in Figure~\ref{fig:block-model}. They
have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey
lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$
(cube, North-West). As there are no analytical solutions for this model we show
the normalized difference between different codes, instead of the relative
error, where the normalized difference of two responses $p$ and $q$ is given by
%
\begin{equation}
  \mr{NRMSD~(\%)} = 200 \frac{|p - q|}{|p| + |q|}\ .
  \label{eq:nrmsd}
\end{equation}
%
\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too
cluttered, and I don't think it would add a lot insights. My idea is therefore
to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones),
and \emg3d/\custem (a cross-comparison). What do you think?}

\imycom[RR]{Agreed. Another suggestion, I solved this visualization problem
  with a color coded matrix plot, showing 90th percentiles or median values of
  all errors along the line as meaningful comprehensive number. Look in my
  thesis - example 4. Comparison for real and imag could be in the lower and
  upper triangles, or we show absolute magnitudes for layered earth in lower
  triangle and for block model in upper triangle. With help of this plot, one
  could easily say if differences are higher for block model and which codes
  fit to each other well.}

\imycom[RR]{If using the mentioned matrix plots, we would need only one of the
  figures 4-6, and could show the other data comprehensively. I added a python
  script to generate an example of my plotting suggestion in the model-block
  directory and a new Figure 7 in the manuscript that illustrates what I mean.
  Of course, any upgrade suggestion for this initial idea is welcome, aside
  from making it looking nice with labels  and annotations.}

@@

The difference becomes only significant at offsets larger than 8\,km. This is
due to a practical difference in the meshing: This simple block model is
advantageous for FV codes, as it consists of rectangular blocks and horizontal
layers, simple geometric objects. While having a very thin, shallow layer is
straight-forward for FV codes, it requires many cells for a FE code. The thin
layer was therefore limited in its horizontal extent to\mycom[DW]{Raphael, to
what x/y exactly?} ???. This is the reason for the increased NRMSD at large
offsets, and it has nothing to do with the accuracy of the computation
itself.\mycom[RR]{see imycom below figure 6}

\imycom[RR]{60 x 60 km (30 km in each direction from center). I already added a
  paragraph about mesh generation in the beginning, I suggest to remove this
  description here and jsut refer to like "Similar to the layered earth model,
  the largest errors occur at offsets $>8$\,km due to the differences in mesh
  design." We should also mention that relative errors are related to the
  magnitudes, as real is so much weaker at larger offsets, it is clear that
  errors increase significantly. Alternatively, we could show absolute
  magnitude or phase errors such as in the Marlim model.}

%
\plot*{median-stats-block}{width=\textwidth}{
    Overall misfit relations between all codes for the three receiver lines
    y=-3, y=0, and y=3 (f.l.t.r.). Colors indicate the median values of the 101
    calculated NRMSD arguments for each line between all codes. Errors for real
    parts are shown in the lower triangle, for imaginary parts in the upper
  triangle.
}
%

@@

The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in
the north-eastern part of the Campos Basin, offshore Brazil, which was
discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well
log data a realistic resistivity model with vertical transverse isotropy (VTI),
Marlim R3D (MR3D), which they released under an open-source license.
\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to
1.25\,Hz, released under an open-source license. To compute the data they used
a state-of-the-art code from the industry \citep{GEO.07.Maao}. It is therefore
an ideal case to verify our open-source codes against, as it is a complex,
realistic model and the data were computed by an industry-proofed
code.\mycom[RR]{I would delete this sentence, not that important and a bit
redundant} Additionally, that code is a time-domain code, whereas the four
codes under consideration here compute the results all in the frequency-domain.

@@

\imycom[RR]{I used gmt the last time 7 years ago , in between I tried the
  gmt4py tools, but they did not work well on my machine. I suggest to use two
  plots next to each other, a similar figure as in the notebook and a simple
  x-y coord sketch (identical extent as the bird perspective view in the other
  plot) with all Tx / Rx locations, highlighting the relevant line and Rx for
  us.}

%
\plot*{model-marlim}{width=\textwidth}{
  This figure obviously needs to be improved massively (at least a colorbar).
  What would you like to show from the actual data here?
  A nice figure would  be Figure 2 in \cite{GEO.19.Correa}; however, note that
  the drawn survey line in that figure are plainly wrong. If someone is
  familiar with GMT and happy to make that would be great. Also, the
  cross-section is currently heavily vertically exaggerated.
}
%

@@

\imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
collaboratively at the same time?}

\imycom[RR]{if you prefer ok, but I don't think this is necessary, if everyone
  adds the own thoughts when he receives the manuscript. Same for conclusions.
  We need to take care to not mix discussion and conclusions, some of the
  statements from here belong rather to the conclusions, I hope it's fine that
  I reorganized the content. Aside from that, I already added all thoughts of
  mine.}

>>>>

% Remove once done
\usepackage[textsize=footnotesize, textwidth=2.8cm]{todonotes}
% \usepackage[textsize=footnotesize, textwidth=2.8cm, disable]{todonotes}

@@

\itodo{
  For comments in the margin, use:\\[.2cm]
  \qquad\texttt{\textbackslash mycom[YOURINITIALS]\{comment\}}\\[.2cm]
  and for inline comments, use:\\[.2cm]
  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}\\[.5cm]
  If you want to compile it without comments, comment the line\\[.2cm]
  \qquad\texttt{\textbackslash usepackage[textsize=footnotesize, textwidth=2.8cm]\{todonotes\}}\\[.2cm]
  and uncomment the line\\[.2cm]
  \qquad\texttt{\% \textbackslash usepackage[textsize=footnotesize, textwidth=2.8cm, disable]\{todonotes\}}
}

@@

\imycom[RR]{We need to take care to not mix British English with AE, I'm very
  used to AE, but Dieter started with (at least what I can identify) mainly BE,
  so I tried to follow (mainly s instead of z and ou instead of o in some
  words). I hope there are not too many inconsistencies, as probably Lindsey
  has to fix all these mistakes in the end:-)
\imycom[DW]{Be aware of Canadian English and Australian English :-D -- You are
  of course right. I am usually mostly BE, having done my PhD in Scotland.
  However, I don't think it matters at the moment, because it will depend to
  what journal we submit. With an appropriate spellchecker that should be a
  quick thing then.}}

Controlled-source electromagnetic (CSEM) measurements are a frequently applied
method in various geophysical exploration fields, such as geothermal and
groundwater, oil and gas, mining, civil engineering, or geo-hazards. Modelling
these electromagnetic fields is therefore of great interest to design survey
layouts, to understand the measured data, and for inversion purposes.
Publications regarding 3D modelling in electromagnetic methods started to
appear as early as the 1970's and 1980's. These early publications were
integral equation (IE) methods, having an anomaly embedded within a layered
medium, mostly for loop-loop type transient EM measurements
\citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and
magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.

@@

Probably the main reason for the numerous amount of code developments was
already outlined by \cite{SG.05.Avdeev}, who finished his review with the
following statement: «\emph{The most important challenge that faces the EM
community today is to convince software developers to put their 3-D EM forward
and inverse solutions into the public domain, at least after some time. This
would have a strong impact on the whole subject and the developers would
benefit from feedback regarding the real needs of the end-users.}» Some major
exploration service companies as well as certain research consortia and
research groups have their own 3D CSEM codes, but how about codes that are
open-source? Academic codes were traditionally often available upon request by
authors. Codes distributed that way were often provided with the request to not
share the code, and they often come without a license attached which means that
they are, legally, not open-source. Also, at times there can be significant
hurdles to install a code.

The meaning of the term open-source evolved rapidly in the last two decades.
Today, open-source generally not only means that a code is available (with a
proper license), but also that the code is hosted online, is under version
control, has the possibility to file issues and make pull requests to fix bugs.
These are important requirements for reproducible research «\emph{to provide
the means by which the reader can verify the validity of the results and make
use of them in further research}» \citep{GEO.17.Broggini}. Well maintained
codes often have continuous integration that includes testing of the code base
and online hosted documentation, often including examples and tutorials. As
such, the term has shifted from purely open-source codes to developments in the
open with increasingly building a global community. Related projects within the
realm of geophysical exploration are e.g., \texttt{pyGIMLi}
\citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}.
\imycom[DW]{Others coming to your mind?\imycom[RR]{no thoughts about geophysics,
  but there are many projects for related topics such as gmt, gis, mesh-gen}}

@@

We simulate EM fields for a layered background model with vertical transverse
isotropy, containing three blocks, and the complex marine Marlim R3D model.
These two model designs as well as the corresponding results from four
different codes provide a benchmark for new codes to be compared to and
validated with. In the following section, we introduce the codes under
consideration. Afterwards, we present the considered benchmark cases in detail
and present the modeling results of our four codes in terms of accuracy and
computational performance. Beyond that, we extensively discuss important points
that control the performance and suitability of our FD and FE codes, including
mainly considerations about the mesh design and the choice of solvers. We
conclude with a summary of our results and a motivation for the EM community to
not only continue to extend the landscape of open-source codes but to also
create a landscape of open-source benchmark models.

\imycom[RR]{Regarding
  \todo[inline, color=white]{
  "It is worth mentioning that there are many more 3D EM
  codes developed in other fields than geophysics such as communication systems
  (antennas, radar, satellites), medical imaging, or civil engineering. There
  are various open-source codes in these fields too, e.g., Elmer
  (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't
  find a publication, just a poster).
  \todo[inline, color=gray]{(\textbf{[DW]}: Add 2-3 proper references)}
  While these codes could potentially be used for the same goals as presented
  here we restrict our review to codes purpose-built and ready without further
  adjustments for geophysical applications."
}
  I thought a lot about this but I just think the previous paragraph is not
  required in our introduction and haven't find a location where it fits
  considering different logical structures. I think it is also not important
  for this paper to tell "that there are more codes in EM than only
  geophysics", that's quite obvious. Maybe delete or shorten to 1 sentences to
  add Elmer and place this sentence somewhere else? I think, an appropriate
  list of all non-geophysical open-source EM codes should be very long anyway,
  we just don't know them or at least I'm not familiar with them.}

@@

\tabl[btp]{codecomparison}{Comparison of the four codes under consideration.
  Note that \emg3d is a solver on its own, while the other codes implement
  third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar},
  \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO}
  \citep{FGCS.04.Schenk}.
}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & PMC; PEC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

We computed the responses for two different models to verify that all different
3D codes yield the same electromagnetic responses. The first simple \emph{Block
model} consists of a layered, anisotropic background with three embedded
blocks. The second Marlim R3D model is based on a very complex, realistic
marine CSEM setup.

\subsection{Block Model}

@@

Figure~\ref{fig:results-layered-0} illustrates the inline responses in the
top-row for offsets $r>0.5\,$km. We only show the semi-analytical result for
the real and imaginary amplitudes. The bottom row displays the relative error
of the 3D codes. The results show that all codes are yielding accurate result
with errors of around 1\,\% in most parts and overall below a few percent,
disregarding locations affected by sign reversals. The differences can be
mainly attributed to the chosen discretisations. The FE codes show the
strongest misfits at large offsets, most likely caused by the utilized boundary
mesh. Very low errors at large offsets are achieved by \emg3d, whereas it
suffers at short offsets from a coarse grid.
%
\plot*{results-layered-0}{width=.8\textwidth}{
   Comparison of the layered model for the inline receivers ($y=0\,$km).
   Top row shows the semi-analytical responses from \empymod, and bottom row
   shows the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
}
%

@@

In a second step, three resistive blocks were added in the 3.3\,km-thick,
anisotropic background layer as shown in Figure~\ref{fig:block-model}. They
have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey
lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$
(cube, North-West). As there are no analytical solutions for this model we show
the normalized difference between different codes, instead of the relative
error, where the normalized difference of two responses $p$ and $q$ is given by
%
\begin{equation}
  \mr{NRMSD~(\%)} = 200 \frac{|p - q|}{|p| + |q|}\ .
  \label{eq:nrmsd}
\end{equation}
%
\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too
cluttered, and I don't think it would add a lot insights. My idea is therefore
to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones),
and \emg3d/\custem (a cross-comparison). What do you think?

\imycom[RR]{Agreed. Another suggestion, I solved this visualization problem
  with a color coded matrix plot, showing 90th percentiles or median values of
  all errors along the line as meaningful comprehensive number. Look in my
  thesis - example 4. Comparison for real and imag could be in the lower and
  upper triangles, or we show absolute magnitudes for layered earth in lower
  triangle and for block model in upper triangle. With help of this plot, one
  could easily say if differences are higher for block model and which codes
  fit to each other well.}
\imycom[RR]{If using the mentioned matrix plots, we would need only one of the
  figures 4-6, and could show the other data comprehensively. I added a python
  script to generate an example of my plotting suggestion in the model-block
  directory and a new Figure 7 in the manuscript that illustrates what I mean.
  Of course, any upgrade suggestion for this initial idea is welcome, aside
  from making it looking nice with labels  and annotations.}
}

@@

The difference becomes only significant at offsets larger than 8\,km. This is
due to a practical difference in the meshing: This simple block model is
advantageous for FV codes, as it consists of rectangular blocks and horizontal
layers, simple geometric objects. While having a very thin, shallow layer is
straight-forward for FV codes, it requires many cells for a FE code, and
a similar approach as for the Block Model was used. This is the reason for the
increased NRMSD at large offsets, and it has nothing to do with the accuracy of
the computation itself.

%
\plot*{median-stats-block}{width=\textwidth}{
  {\imycom[DW]{Suggestion from Raphael for a statistics plot.}}
    Overall misfit relations between all codes for the three receiver lines
    y=-3, y=0, and y=3 (f.l.t.r.). Colors indicate the median values of the 101
    calculated NRMSD arguments for each line between all codes. Errors for real
    parts are shown in the lower triangle, for imaginary parts in the upper
  triangle.
}
%

@@

The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in
the north-eastern part of the Campos Basin, offshore Brazil, which was
discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well
log data a realistic resistivity model with vertical transverse isotropy (VTI),
Marlim R3D (MR3D), which they released under an open-source license.
\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to
1.25\,Hz, released under an open-source license. To compute the data they used
a state-of-the-art code from the industry \citep{GEO.07.Maao}. It is therefore
an ideal case to verify our open-source codes against, as it is a complex,
realistic model and the data were computed by an industry-proofed
code. Additionally, that code is a time-domain code, whereas the four codes
under consideration here compute the results all in the frequency-domain.
\imycom[RR]{I would delete this sentence, not that important and a bit
redundant.\imycom[DW]{Did you refer to the last sentence or the one before? I
think the last sentence contains quite important info.}}

@@

%
\plot*{model-marlim}{width=\textwidth}{
  This figure obviously needs to be improved massively (at least a colorbar).
  What would you like to show from the actual data here?
  A nice figure would  be Figure 2 in \cite{GEO.19.Correa}; however, note that
  the drawn survey line in that figure are plainly wrong.
  {\imycom[DW]{If someone is
  familiar with GMT and happy to make that would be great. Also, the
cross-section is currently heavily vertically exaggerated.
\imycom[RR]{I used gmt the last time 7 years ago , in between I tried the
  gmt4py tools, but they did not work well on my machine. I suggest to use two
  plots next to each other, a similar figure as in the notebook and a simple
  x-y coord sketch (identical extent as the bird perspective view in the other
  plot) with all Tx / Rx locations, highlighting the relevant line and Rx for
  us.}}}
}
%

@@

\imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
collaboratively at the same time?
\imycom[RR]{if you prefer ok, but I don't think this is necessary, if everyone
  adds the own thoughts when he receives the manuscript. Same for conclusions.
  We need to take care to not mix discussion and conclusions, some of the
  statements from here belong rather to the conclusions, I hope it's fine that
  I reorganized the content. Aside from that, I already added all thoughts of
  mine.}
}
